\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-5pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSmallSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}
\newcommand{\resumeCertification}[3]{
  \item \small{
    \textbf{#1}{ - #2 \hfill #3 \vspace{-5pt}}
  }
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-2pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{{\LARGE Satyam Sagar}} & Email:~~\href{mailto:}{satyamsagar1711@gmail.com}\\
    Portfolio:~~\href{https://satyamrs00.github.io}{https://satyamrs00.github.io} & Mobile:~~+91 979 8581 008 \\
    Github:~~\href{https://github.com/satyamrs00}{https://github.com/satyamrs00} &  LinkedIn:~~\href{https://linkedin.com/in/satyamrs00}{https://linkedin.com/in/satyamrs00}\\
    % Codechef:~~\href{https://codechef.com/users/satyamrs00}{https://satyamrs00} &
    Leetcode:~~\href{https://leetcode.com/satyamrs00}{https://leetcode.com/satyamrs00}\\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading{Indian Institute of Information Technology}{Bhopal, India}
      {Bachelor of Technology - Information Technology;  GPA: 9.35/10}{December 2021 - June 2025}
      \vspace{-3pt}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Data Structures and Algorithms, Object Oriented Programming, Database Management Systems}}}
      %, Operating Systems,  Artificial Intelligence, Machine Learning, Networking, Databases
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading{GreyFeathers}{Dec 2022 - present}
    {Frontend Developer Intern}{}
    \begin{description}[font=$\bullet$]
    \item {Worked on 3+ projects at various stages. Integrated the UI with server APIs. Used React and Redux for frontend.}
    \vspace{-4pt}  
    \item {Resolved 60+ client requests. Provided support and maintenance for the existing projects.}
    \vspace{-4pt}
    \item {Converted 100+ figma designs to React components using Material UI and Tailwind CSS and third party libraries.}
    \vspace{-4pt}
    \item {Implemented Google OAuth and JWT authentication. Used Trello for project management.}
    \vspace{-4pt}
    \item {Troubleshooted cross-browser compatibility and dependencies issues to increase the website's reach by 25\%.}
    \end{description}

    \resumeSubheading{JDMR Ischool}{Oct 2022 - Dec 2022}
    {Web Developer Intern}{}
    \begin{description}[font=$\bullet$]
		\item {Teamed up with 2 other interns to develop a Django application from scratch. Worked on 2 main projects.}
		\vspace{-4pt}
		\item {Developed a clean and responsive UI using Bootstrap. Made use of Django templates and Jinja templating engine.}
		\vspace{-4pt}
		\item {Deployed the applications using DigitalOcean with Nginx server and secured it using Let's Encrypt.}
    \end{description}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart

    \resumeSmallSubheading{\textbf{Pinocchio's Pizza - Django \textbar} ~\href{https://github.com/pizza/}{github} \textbar ~\href{https://pizza-uyud.onrender.com/}{demo}}{August 2022}

    
    \begin{description}[font=$\bullet$]
        \item {Pinocchio's Pizza is a online front for a pizza shop. Supports online ordering, user management and order tracking.}
    \vspace{-5pt}
        \item {Unique relational database for highly customizable orders with upto 5 toppings, 2 sizes, and multiple add-ons.}
    \vspace{-5pt}
        \item {Supports email notifications using gmail smtp. Uses cloud storage via Cloudinary. Deployed on Render, Heroku.}
    % \vspace{-5pt}
        % \item {Feature to view previous orders and order status. Also feature for 1-click reorder your favorite order.}
    \end{description}

    \vspace{-5pt}
    
    \resumeSmallSubheading{\textbf{Drumzz - React \textbar}~\href{https://github.com/satyamrs00/drum}{github} \textbar ~\href{https://drumzz.netlify.app}{demo}}{December 2022}

    \begin{description}[font=$\bullet$]
        \item {Drumzz is a keyboard drum kit react application. It is a fun application to play music using your keyboard.}
    \vspace{-5pt}
        \item {Support for multiple drum systems and volume control. Also supports mouse clicks and touch events.}
    \end{description}

    \vspace{-5pt}
    
    \resumeSmallSubheading{\textbf{Password Guy - Flask \textbar}~\href{https://github.com/satyamrs00/password_guy}{github}}{April 2022}
    
    \begin{description}[font=$\bullet$]
        \item {Password Guy is a password manager application built using Flask and SQLite.}
    \vspace{-5pt}
        \item {Supports user authentication and password encryption. Designed and developed the UI using Bootstrap.}
    \end{description}
    
\resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~ Python, Javascript, SQL, Bash, C, C++, HTML, CSS}
	\resumeSubItem{Frameworks}{~~~~ Django, React, Django REST Framework, Flask}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~ Git, PostgreSQL, SQLite, Postman, MongoDB, Redux, Material UI}
	\resumeSubItem{Platforms}{~~~~~~~ Linux, Web, Windows, Heroku, GCP, DigitalOcean, Netlify}
	\resumeSubItem{Soft Skills}{~~~~~~~ Leadership, Collaboration, Management, Communication}

\resumeSubHeadingListEnd

\vspace{-2pt}
\section{Achievements}
\begin{description}[font=$\bullet$]
    \item {3 star at CodeChef with 1627 rating (max)}
    \vspace{-7pt}
    \item {Scored rank 2 with my team at HackSquad which had 750+ team registrations - October, 2022}
    \vspace{-7pt}
    \item {Scored rank 4 in college at Codame Things, that is an annual coding competition by Codame Club - July, 2022}
\end{description}
\vspace{-5pt}
\section{Certifications}
\resumeSubHeadingListStart
    \resumeCertification
    {Javascript algorithms and data structures}
    {freeCodeCamp}{\href{https://www.freecodecamp.org/certification/satyamrs00/javascript-algorithms-and-data-structures}{show credential}}

    \resumeCertification
    {Relational Databases}
    {freeCodeCamp}{\href{https://www.freecodecamp.org/certification/satyamrs00/relational-database-v8}{show credential}}

    \resumeCertification
    {Responsive Web Design}
    {freeCodeCamp}{\href{https://www.freecodecamp.org/certification/satyamrs00/responsive-web-design}{show credential}}
    
    \resumeCertification
    {Google Cloud Skill Badges (30 badges, 15 labs)}
    {Google Cloud community India} {\href{https://www.cloudskillsboost.google/public_profiles/979efb3e-91bc-476f-ba38-d35c4879a1fa}{show credential}}

    \resumeCertification
    {CS50x - Introduction to programming}
    {Harvard University}{\href{https://certificates.cs50.io/5a9d3a4b-57f0-4d46-95fa-222159e1368f.pdf?size=letter}{show credential}}
    
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Positions of Responsibility}
\resumeSubHeadingListStart
    \resumeSubheading
    {GNU/Linux Users Club - IIIT Bhopal}{Bhopal, India}
    {Core team member}{August 2022 - Present}

    \begin{description}[font=$\bullet$]
        \item {Organized 3 events and workshops on Linux and open source. Conducted 2 sessions on Linux and Git.}
        \vspace{-4pt}
    \end{description}
\resumeSubHeadingListEnd

\end{document}