\documentclass[a4paper,10pt]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\raggedbottom
\raggedright

% Section spacing (tight but safe)
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

% List spacing (key to 1-page without overlap)
\setlist[itemize]{itemsep=1pt, topsep=3pt, leftmargin=*}
\setlist[description]{itemsep=1pt, topsep=3pt}

\setlength{\tabcolsep}{0in}

%-------------------------
% Custom commands

\newcommand{\resumeSubheading}[4]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{#3} & \textit{#4} \\
\end{tabular*}
}

\newcommand{\resumeSmallSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
#1 & #2 \\
\end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\item \small{\textbf{#1}: #2}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-----------------------------

\begin{document}
\small

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\Large Satyam Sagar} & \\
LinkedIn:~~\href{https://linkedin.com/in/satyamrs00}{https://linkedin.com/in/satyamrs00} & Leetcode:~~\href{https://leetcode.com/u/satyamrs00}{https://leetcode.com/u/satyamrs00}\\
Email:~~\href{mailto:satyamsagar1711@gmail.com}{satyamsagar1711@gmail.com} & Codechef:~~\href{https://codechef.com/users/satyamrs00}{https://codechef.com/users/satyamrs00}\\
Mobile:~~+91 9798581008 & Github:~~\href{https://github.com/satyamrs00}{https://github.com/satyamrs00}\\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading{UKG}{Jul 2025 - Present}{Software Engineer}{}
\begin{itemize}
\item Ensured smooth rollouts while processing \textbf{more than 10 releases} as a part of the Customs team.
\item Built internal tools and features for \textbf{Angular and DotNet} microservice-based automation system, improving efficiency.
\item Built an AI-powered merge tool, automating merge conflict resolution and reducing workflow processing time by \textbf{10\%}.
\item Diagnosed and resolved frontend and backend bottlenecks across deployment-monitoring dashboards, reducing API response times \textbf{by up to 93\%} and cutting 1000-record bulk processing time from 380s to 4s.
% \item Monitored deployment logs on Splunk for customs packages and resolved \textbf{more than 25 defects}.
\item Leveraged AI to generate unit test cases for legacy .NET services, achieving \textbf{over 70\% code coverage}.
\end{itemize}

\resumeSubheading{Cred}{Sep 2024 - Apr 2025}{Software Engineer Intern}{}
\begin{itemize}
\item Designed and developed scalable backend utility services to streamline storage, maintenance, and tracking of test cases for entire organization resulting in more than \textbf{90\% reduction in Testrail costs}.
\item Automated more than 30 E2E test cases for REST APIs using TestNG and Java, increasing coverage by \textbf{50\%}.
\item Automated more than 40 E2E test cases for Android and iOS applications using Appium and Java client.
\end{itemize}

\resumeSubheading{Infinity Learn}{Oct 2023 - Dec 2023}{Software Engineer Intern}{}
\begin{itemize}
\item Implemented staging CI/CD pipelines utilizing \textbf{AWS Amplify}, reducing deployment time by 30\%.
\item Optimized SEO, accessibility, and responsiveness, successfully supporting monthly user \textbf{traffic of 500,000}.
\end{itemize}

\resumeSubheading{GreyFeathers}{Dec 2022 - Oct 2023}{Software Engineer Intern}{}
\begin{itemize}
\item Developed user interfaces and integrated server APIs using React and Redux, enhancing project functionality.
\item Translated over \textbf{200 Figma designs} into functional React components, employing Material UI and Tailwind CSS.
\item Resolved cross-browser compatibility and dependencies concerns, resulting in a \textbf{25\% boost in website traffic}.
\item Addressed and resolved over 60 client issues, ensuring consistent support and maintenance for established projects.
\end{itemize}

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Indian Institute of Information Technology}{Bhopal, India}
{Bachelor of Technology - Information Technology; GPA: 8.55/10}{Dec 2021 - May 2025}
{\scriptsize \textit{\textbf{Courses:} Computer Science, Data Structures and Algorithms, Database Management Systems, Software Engineering, Design Patterns, Object Oriented Programming, Operating Systems, Artificial Intelligence, Discrete Math}}
\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{Java, Python, JavaScript, SQL, Node.js, HTML, CSS, C++, TypeScript, Bash}
\resumeSubItem{Frameworks}{React.js, Flask, Django, Django REST Framework, SQLAlchemy, Express.js}
\resumeSubItem{Tools}{CI/CD, Git, PostgreSQL, NoSQL, DynamoDB, MongoDB, REST APIs, JWT, Testing, Microsoft SQL Server}
\resumeSubItem{Platforms}{AWS, Docker, Kubernetes, Linux, Git/GitHub, Jenkins, Redis, Postman, Splunk, Grafana}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading{\textbf{Ayurmitram} \textbar ~\href{https://github.com/ayurmitram/}{https://github.com/ayurmitram}}{Dec 2023}{Express.js, React.js, Random Forest Classification}{}
\begin{itemize}
\item Programmed an \textbf{AI chatbot} that classifies individual prakruti(phenotype) into 7 distinct categories.
\item Secured sensitive data by implementing encryption and time-limited storage up to 1 week in MongoDB database.
\end{itemize}

\resumeSmallSubheading{\textbf{Backpack} \textbar ~\href{https://github.com/satyamrs00/backpack/}{https://github.com/satyamrs00/backpack} \textbar ~\href{https://main--back-backpack.netlify.app/}{https://main--back-backpack.netlify.app}}{Jan 2023}{Django REST Framework, React.js}{}
\begin{itemize}
\item Built backend REST APIs using Django REST Framework for a resource-sharing platform promoting collaborative book exchanges among college students.
\item Conducted unit and integration testing on over 10 endpoints, utilizing Postman to ensure system reliability.
\end{itemize}

\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------------
\section{Achievements}
\begin{itemize}
\item Attained \textbf{1st place in SIH 2023} by developing an innovative chatbot designed to determine individual phenotypes.
\item Achieved a \textbf{3-star} rating of 1774 on Codechef. Placed in top 4.44\% with a rating of 1906 \textbf{(knight)} on Leetcode.
\item Consistently ranked within the \textbf{top 200} globally in Codechef Starters, with best positions of 99, 126, and 160.
\item Organized 3 workshops emphasising the importance of open source. Reached 500+ students through these events.
\item Secured 2nd place at HackSquad 2022, demonstrating excellence in competitive open-source contribution.
\item Placed 4th in a college-level competitive coding event hosted by the Codame Club at IIIT Bhopal.
\end{itemize}

\end{document}