\documentclass[a4paper,10pt]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\raggedbottom
\raggedright

% Section spacing (tight but safe)
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

% List spacing (key to 1-page without overlap)
\setlist[itemize]{itemsep=1pt, topsep=3pt, leftmargin=*}
\setlist[description]{itemsep=1pt, topsep=3pt}

\setlength{\tabcolsep}{0in}

%-------------------------
% Custom commands

\newcommand{\resumeSubheading}[4]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{#3} & \textit{#4} \\
\end{tabular*}
}

\newcommand{\resumeSmallSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
#1 & #2 \\
\end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\item \small{\textbf{#1}: #2}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-----------------------------

\begin{document}
\small

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\Large Satyam Sagar} & \\
% LinkedIn:~~\href{https://linkedin.com/in/satyamrs00}{https://linkedin.com/in/satyamrs00} & Leetcode:~~\href{https://leetcode.com/u/satyamrs00}{https://leetcode.com/u/satyamrs00}\\
Email:~~\href{mailto:satyamsagar1711@gmail.com}{satyamsagar1711@gmail.com} & LinkedIn:~~\href{https://linkedin.com/in/satyamrs00}{https://linkedin.com/in/satyamrs00}\\
Mobile:~~+91 9798581008 & Github:~~\href{https://github.com/satyamrs00}{https://github.com/satyamrs00}\\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading{UKG}{Jul 2025 - Present}{Software Engineer}{}
\begin{itemize}
\item Eliminated critical performance bottlenecks across deployment-monitoring dashboards through DB-level optimizations (iTVFs, indexes, stored procedures) and Angular rendering improvements (OnPush change detection, trackBy, pure pipes), reducing API response times by up to \textbf{93\%} and bulk processing time from \textbf{380s to 4s}.
\item Established test coverage from zero for $\sim$50 legacy .NET controllers using AI-assisted generation, achieving \textbf{70\%+} coverage across unit and integration tests.
\item Built an AI-powered merge tool that resolves $\sim$1,000 conflicts per sprint, saving \textbf{15 engineering hours} per cycle.
\item Packaged and delivered 10+ customized releases for \textbf{3,000+ clients}, managing per-client configuration layered on top of the base product.
\item Extended the release pipeline to include presales builds, eliminating manual packaging and consolidating all product variants into a single automated process.
\item Built a database cloning utility to replicate production data (6GB) to dev environments in $\sim$40s, used automatically via weekly cron job and on-demand by the team.
% \item Monitored deployment logs on Splunk for customs packages and resolved \textbf{more than 25 defects}.
\end{itemize}

\resumeSubheading{Cred}{Sep 2024 - Apr 2025}{Automation Engineer Intern}{}
\begin{itemize}
\item Built internal test case management services in Java, consolidating org-wide TestRail usage from \textbf{25+ accounts to 1}, reducing licensing costs by over 90\%.
\item Expanded E2E test coverage for the Lending-as-a-Service module by \textbf{200\%} (\textbf{15 to 45} multi-step scenarios) across REST APIs and iOS using TestNG, Java, and Appium.
\end{itemize}

\resumeSubheading{Infinity Learn}{Oct 2023 - Dec 2023}{Software Engineer Intern}{}
\begin{itemize}
\item Set up staging CI/CD pipelines on AWS Amplify, reducing deployment time by 30\%.
\item Improved Lighthouse Performance score from \textbf{$\sim$40 to 80+} through frontend optimizations including faster time-to-first-paint, reduced layout shifts, and SEO and accessibility fixes.
\end{itemize}

\resumeSubheading{GreyFeathers}{Dec 2022 - Oct 2023}{Software Engineer Intern}{}
\begin{itemize}
\item Built and shipped frontend features across 2 products — a QR-based restaurant POS system and an AI research tool (PDF upload, QnA, note-taking) — using React, Redux, and Tailwind CSS.
\item Implemented 200+ Figma designs as production React components, maintaining design fidelity across both products.
\end{itemize}

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading{\textbf{Ayurmitram} \textbar ~\textnormal{\href{https://github.com/ayurmitram/}{https://github.com/ayurmitram}}}{Dec 2023}{Express.js, React.js, Random Forest Classification}{}
\begin{itemize}
\item Built an Ayurvedic phenotype classifier combining an LLM-driven conversational intake (20 questions, one at a time) with a Random Forest model to predict prakruti across 7 categories — won 1st place at Smart India Hackathon 2023.
\item Secured user data with encryption and TTL-based auto-deletion (7 days) in MongoDB.
\end{itemize}

% \resumeSmallSubheading{\textbf{Backpack} \textbar ~\href{https://github.com/satyamrs00/backpack/}{https://github.com/satyamrs00/backpack} \textbar ~\href{https://main--back-backpack.netlify.app/}{https://main--back-backpack.netlify.app}}{Jan 2023}{Django REST Framework, React.js}{}
% \begin{itemize}
% \item Built backend REST APIs using Django REST Framework for a resource-sharing platform promoting collaborative book exchanges among college students.
% \item Conducted unit and integration testing on over 10 endpoints, utilizing Postman to ensure system reliability.
% \end{itemize}

\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------------
\section{Achievements}
\begin{itemize}
\item Won \textbf{1st place at Smart India Hackathon 2023} among thousands of national teams for an Ayurvedic phenotype classifier.
\item Ranked 2nd at HackSquad 2022 out of 200+ teams by leading the most open-source PR merges during Hacktoberfest.
\item Rated Knight (1906) on Leetcode (top 4.44\%) and 3-star (1774) on Codechef; consistently ranked top 200 globally in Codechef Starters (best: 99th).
\item Organized 3 open-source workshops through the GNU/Linux Users Club, reaching 500+ students on campus.
\end{itemize}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Indian Institute of Information Technology}{Bhopal, India}
{Bachelor of Technology - Information Technology; GPA: 8.55/10}{Dec 2021 - May 2025}
{}
% {\scriptsize \textit{\textbf{Courses:} Computer Science, Data Structures and Algorithms, Database Management Systems, Software Engineering, Design Patterns, Object Oriented Programming, Operating Systems, Artificial Intelligence, Discrete Math}}
\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{Java, C\#, TypeScript, JavaScript, Python, SQL, Bash, C++}
\resumeSubItem{Frameworks}{React.js, Angular, Express.js, Django REST Framework, Flask, Node.js}
\resumeSubItem{Databases}{PostgreSQL, MongoDB, Microsoft SQL Server, Redis}
\resumeSubItem{Tools}{Git, TeamCity, Jenkins, Docker, Kubernetes, AWS (S3, Secrets Manager), Retool, Postman, Splunk, Grafana}
\resumeSubItem{Concepts}{REST APIs, CI/CD, JWT, Microservices, Unit \& Integration Testing, GitHub Actions}
\resumeSubHeadingListEnd

\end{document}